\PassOptionsToPackage{table,xcdraw}{xcolor}

\documentclass[sigconf,review,anonymous]{acmart}
\acmConference[ESEC/FSE 2022]{The 30th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering}{14 - 18 November, 2022}{Singapore}

%\documentclass[sigconf,review,anonymous]{acmart}
%\acmConference[ESEC/FSE 2021]{The 29th ACM Joint European Software Engineering Conference and Symposium on the Foundations of Software Engineering}{23 - 27 August, 2021}{Athens, Greece}

%\acmConference[ICSE 2022]{The 44th International Conference on Software Engineering}{May 21–29, 2022}{Pittsburgh, PA, USA}

%\documentclass[sigconf,review, anonymous]{acmart}
%\documentclass[sigconf]{acmart}

\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{array}
\usepackage{amsmath,amsfonts}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
%\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{float}
\usepackage{listings}
\usepackage{xspace}
\usepackage{multirow}
\usepackage{amsthm}
\newtheorem{definition}{Definition}
\usepackage{balance}

\usepackage[skins]{tcolorbox}

\usepackage{xcolor,pifont}
\newcommand*\colourcheck[1]{%
	\expandafter\newcommand\csname #1check\endcsname{\textcolor{#1}{\ding{52}}}%
}
\colourcheck{blue}
\colourcheck{green}
\colourcheck{red}

\newtcolorbox{myframe}[2][]{%
  enhanced,colback=white,colframe=black,coltitle=black,
  sharp corners,
  toprule=1.0pt,
  rightrule=0.3pt,
  leftrule=0pt,
  bottomrule=0pt,
  fonttitle=\itshape\scshape\large,
  left=0pt,right=5pt,top=5pt,bottom=3pt,
  attach boxed title to top right={yshift=-0.3\baselineskip-0.4pt,xshift=-5mm},
  boxed title style={tile,size=minimal,left=0.2mm,right=0.5mm,
    colback=white,before upper=\strut},
  title=#2,#1
}

%\newcommand{\code}[1]{{\footnotesize\textsf{#1}}}

\newcommand{\tool}{\textsc{UTango}\xspace}

\newcommand{\mvpdg}{$\delta$-PDG$^{i,j}$}

\newtheorem{Definition}{Definition}
\newtheorem{Claim}{Claim}
\newtheorem{Lemma}{Lemma}
\newtheorem{Theorem}{Theorem}

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newtheorem{observation}{Observation}
\newtheorem{property}{Property}
\newcommand{\code}[1]{{\footnotesize\texttt{#1}}}
\usepackage{amsthm}
 \definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=left,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=4
}



\begin{document}

%\title[{\tool}: Deep Fault Localization with Code Coverage Representation Learning]{{\tool}: Deep Fault Localization with Code Coverage Representation Learning}

\title[Untangling Commits with Context-aware, Graph-based, Code Change Clustering Learning Model]{{\tool}: Untangling Commits with Context-aware,\\ Graph-based, Code Change Clustering Learning Model}

%Context-aware
%ML
%Clone-aware
%Graph-based


%%%---- AUTHORS BLOCK ------

\setcopyright{none}

\settopmatter{printacmref=false, printfolios=false}

\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column


%(1) present information sorted in a way that a CNN can "see" patterns
%discriminating between faulty and non faulty statements more easily;

%(2) identify the actual crash statement to the network;

%(3) present more information to the deep neural network in the form of
%a summary of data dependence for each statement as well as source
%embedding; and

%(4) the suspiciousness of a statement is seen taking into account
%relationships to other statement, as opposed to a statement by itself”



%\input{sections/abstract}
\begin{abstract}
During software evolution, developers make several changes and commit
them into the repositories. Unfortunately, many of them tangle
different purposes, both hampering program comprehension and reducing
separation of concerns. Automated approaches with deterministic
solutions have been proposed to untangle commits.
%Unlike the state-of-the-art, deterministic untangling approaches,

In this work, we present {\bf \tool}, a machine learning (ML)-based
approach that learns to untangle the changes in a commit.
%
We develop a {\em novel code change clustering learning model} that
learns to cluster the code changes, represented by the embeddings,
into different groups with different concerns.
%
We adapt the agglomerative clustering algorithm into a
supervised-learning clustering model operating on the learned code
change embeddings via trainable parameters and a loss function in
comparing the predicted clusters and the correct ones during training.
%
%Another key idea of {\tool} is
To facilitate our clustering learning model, we develop a {\em
context-aware, graph-based, code change representation learning
model}, leveraging Label, Graph-based Convolution Network to produce
the {\em contextualized embeddings for code changes}, that integrates
program dependencies and the surrounding contexts of the changes. The
contexts and cloned code are also explicitly represented, helping
{\tool} distinguish their concerns.
%
Our empirical evaluation on a public C\# dataset
with 1,612 tangled commits shows that it achieves the
accuracy of 28.6\%--462.5\%, relatively higher than the
state-of-the-art approaches in clustering the changed code. We also
evaluated {\tool} in a Java dataset with 14k+ tangled commits. The result shows
that it achieves 13.3\%-100.0\% relatively higher accuracy than the
state-of-the-art approaches.

%Our sensitivity also shows that all designed components in {\tool}
%contributes positively to its high accuracy.}
\end{abstract}

%\textcolor{red}{Our empirical evaluation on a real-world C\# dataset
%with 21k commits and 1,612 concerns shows that it achieves the
%accuracy of XX.X\%--XX.X\% and YY.Y\%--YY.Y\% relatively higher than
%the state-of-the-art approaches in cross-project and within-project
%settings. We also evaluated {\tool} in a Java dataset with XX
%commits. The results show that it achieves accuracy XX.X\% relatively
%higher than the state-of-the-art approach.  Our sensitivity also shows
%that all designed components in {\tool} contributes positively to its
%high accuracy.}

%We develop a novel code change representation learning model
%leveraging Graph-based Convolution Network to build the vector
%representations for the changes, which integrate program dependencies,
%the surrounding contexts of the changes, as well as the code clone
%relationships.

%\settopmatter{printacmref=true, printccs=true, printfolios=false}

%\begin{CCSXML}
%<ccs2012>
%<concept>
%<concept_id>10011007.10011006.10011073</concept_id>
%<concept_desc>Software and its engineering~Software maintenance tools</concept_desc>
%<concept_significance>500</concept_significance>
%</concept>
%</ccs2012>
%\end{CCSXML}

%\ccsdesc[500]{Software and its engineering~Software maintenance tools}

%\keywords{Deep Learning; Automated Program Repair; Context-based Code Transformation Learning}


\maketitle

\input{sections/intro}

\input{sections/motiv}

\input{sections/overview}

\input{sections/approach_step_2}

\input{sections/appraoch_step_3}

\input{sections/emperical}

\input{sections/related}

\input{sections/conclusion}

\newpage

\balance

%\bibliographystyle{plain}
%\bibliographystyle{ACM-Reference-Format}
\bibliographystyle{ACM-Reference-Format}

\bibliography{References}

\end{document}
