%\vspace{-12pt}
\subsection{Key Ideas}
\label{ideas:sec}

From the motivation, we propose {\tool} with the following
ideas.

%{\bf Key Idea 1 [Code Change Representation Learning with Graph
%    Convolution Network (GCN)]}.

\vspace{2pt}
{\bf Key Idea 1 [Code Change Clustering Learning Model]}. Instead of
deciding a deterministic clustering criterion on the concrete
artifacts (PDGs, program slices, code changes, operations, or change
graphs), from Observation 1, we build an ML model to untangle the
commits by learning to cluster code~changes represented by embeddings,
w.r.t. different concerns. The model learns from the~history of the
co-changed statements in the same commits for the same concerns, and
applies to cluster the changes in the current commit.  We also modify
an agglomerative clustering algorithm into a~super\-vised-learning
clustering model via trainable parameters and a loss function to
compare the predicted clusters and the correct ones.

\vspace{3pt} {\bf Key Idea 2 [Context-aware, Graph-based
    Representation Learning for Code Changes].} We design a
context-aware, graph-based, representation learning model to {\em
  learn the contextualized embeddings for the code changes}
that integrates {\em program dependencies} among the program elements,
and the {\em contexts} of~code changes. We train a Label, Graph-based
Convolution Network~\cite{label-gcn} to learn~the embeddings and learn
to cluster them from the history.
%of changed code for the same concerns.
For prediction, we apply supervised-learning agglomerative clustering
on~the embeddings of code changes to produce the clusters to untangle
the commit. We expect that supervised-learning clustering on vectors
is more effective than on those artifacts since the embeddings
capture~richer information integrated from dependencies and
contexts.

\vspace{3pt}
{\bf Key Idea 3 [Explicit Context Representation as a Weight to
    Compute Vectors for Code Changes]}. As in Observation 2, the
contexts of the code changes can help distinguish their concerns in
the commits. We represent code changes and the surrounding context of
a change via the multi-version program dependence~graph,
$\delta$-PDG~\cite{flexeme-fse20}, consisting of the elements of both
versions before and after the changes, and program dependencies. The
context is defined as the surrounding nodes of the changed statement
node~in~that graph. The Label-GCN is used to model the statements and
their dependencies in $\delta$-PDG as well as to learn the vector
representing the context for a change. The context vectors are then
used as weights in learning contextualized embeddings for the code
changes.

\vspace{3pt}
{\bf Key Idea 4 [Implicit Dependencies among Cloned Code]}. As in
Observation 3, the cloned code exhibits implicit dependencies with
regard to whether they can be changed in the same commits for the same
concerns. Thus, during the process of producing the final
result, we also integrate the code clone relationships to
adjust the clusters produced by the clustering learning model.

%Thus, the GCN model can learn the embeddings of the code changes with
%the consideration of the cloned code.
